Evolution of ORM Systems: Formal Foundations

### 2013-01-26 doc/description.tex
updated add association & case study

\paragraph{Add association} Adding an association into a database is complicated because of already existing instances. When an association between classes is added the instances of both classes has to be connected on the database level via foreign key or connection table. The information about pairing has to be provided by the user in form of set of instances pairs, because the model does not contain enough information. 
\begin{align*}
& \mathbf{addAsociation} : Label \times Association \times (Row \times Row) \times State \rightarrow State \\
& \Psi(s, addAsociation(l, a, m_{l_1, l_2})) = application(s) \circ addAssoc(l, a) \\
& \Phi(s, addAsociation(l, a, m_{l_1, l_2})) = \\
& =\begin{cases}
	\inference{ \exists t_s, t_t \in tables(d) : name(t_s) = l\\ 		\wedge name(t_t) = reference(a) \\ \wedge \forall f \in foreignKeys(t_t) \cup columns(t_t) \\: name(f) \neq name(a) \\ startCardinality(a) \leq 1}{\begin{gathered}
		database(s) \\ \bullet addForeignKey(name(t_s), \rho(a,d), d) \\ \bullet \forall r \in m_{l_1, l_2} : \\ insertRow(row(name(t_s), [name(a), \\ value(primaryKey(first(r)))]), d)
	\end{gathered}}
 \\ \\
	\inference{ \exists t_s, t_t \in tables(d) : name(t_s) = l \\ \wedge name(t_t) = reference(a) \\ \wedge startCardinality(a) > 1}{\begin{gathered} 
	database(s) \bullet addTable(\rho(a,d),d) \\ \bullet \forall r \in m_{l, reference(a)} :\\ insertRow(\\ row(name(owningClass(a)) + name(a), \\ [name(t_s), value(primaryKey(first(r)))]\\ [name(t_t), value(primaryKey(second(r)))]))
	\end{gathered}} 
\end{cases}\\
& s \in Software, l_1, l_2 \in Label, m_{l, reference(a)} \wedge l_2 = reference(a)
\end{align*}

@@

\section{Case Study}
The case study demonstrates how the transformation helps with data evolution in real example of software evolution. There are two classes in our software $Person$ and $LegalPerson$ both of them contains information about address (street, city and zip code). To improve the design of code the class Address has to be created which associated with both original classes and contains the data already stored in the software. The initial situation:
\begin{align*}
&	S = sw(a, db(t,r))
\end{align*}
\begin{align*}
a &= app(cl(Person, (pr(surname, APPSTRING, \varnothing), \\
& pr(street, APPSTRING, \varnothing), \\
& pr(city, APPSTRING, \varnothing)), pr(zip, APPSTRING, \varnothing)), \\
& cl(LegalPerson, (pr(businessName, APPSTRING, \varnothing), \\
& pr(street, APPSTRING, \varnothing), \\
& pr(city, APPSTRING, \varnothing)), pr(zip, APPSTRING, \varnothing))
\end{align*}
\begin{align*}
t &= db(tab(Person, pk("Id"), col(surname, APPSTRING, \varnothing, \varnothing), \\
& col(street, APPSTRING, \varnothing, \varnothing), col(city, APPSTRING, \varnothing, \varnothing) \\
& col(zip, APPSTRING, \varnothing, \varnothing), \varnothing), \\
& tab(LegalPerson, pk("Id"),  col(businessName, APPSTRING, \varnothing, \varnothing), \\
& col(street, APPSTRING, \varnothing, \varnothing), col(city, APPSTRING, \varnothing, \varnothing) \\
& col(zip, APPSTRING, \varnothing, \varnothing), \varnothing)) 
\end{align*}
\begin{align*}
r &= row("person", ["Id", 1], ["surname", "Griffin"], \\
& ["street", "S. Mary Evenue 22"], ["city", "NY"], ["zip", 10001]), \\
& row("person", ["Id", 2], ["surname", "Doe"], \\
& ["street", "Olive ave. 2225"], ["city", "LA"], ["zip", 90003]), \\
& row("legalPerson", ["Id", 1], ["businessName", "Tools and Machines ltd."], \\
& ["street", "Hill stret 22"], ["city", "NY"], ["zip", 10001]), \\
& row("legalPerson", ["Id", 2], ["businessName", "Doe"], \\
& ["street", "Pine ave. 2225"], ["city", "LA"], ["zip", 90003]))
\end{align*}
The first evolution step is to create the address class for $Person$ and $LegalPerson$, then the temporary class can be merged together and finally the temporary class has to be renamed to $Address$:
\begin{align*}
& state(S) \oplus Extract("Person", "Address_tmp1", "street", "city", "zip") \\
& \oplus AddAssociation("Person", assoc("address", "Address_tmp1", 1, 1),\\ 
& \{(x,y)| x \in instances("Person", database(S)), \\
& y \in instances("Address_tmp1", database(S)) : pkVal(x) = pkVal(y) \}) \\
& \oplus Extract("LegalPerson", "Address_tmp2", "street", "city", "zip")  \\
& \oplus AddAssociation("LegalPerson", assoc("address", "Address_tmp1", 1, 1),\\ 
& \{(x,y)| x \in instances("LegalPerson", database(S)), \\
& y \in instances("Address_tmp2", database(S)) : pkVal(x) = pkVal(y) \}) \\
& \oplus Merge("Address_tmp1", "Address_tmp2", "Address") \\
& \oplus RemoveTableAndData("Address_tmp1") \\
& \oplus RemoveTableAndData("Address_tmp2")
\end{align*}
The software state after adding the second association is:

@@

\newpage
ExtactClass = addClass
\begin{align*}
a' &= app(cl(Person, (pr(surname, APPSTRING, \varnothing), \\
& pr(street, APPSTRING, \varnothing), \\
& pr(city, APPSTRING, \varnothing)), pr(zip, APPSTRING, \varnothing)), \\
& cl(LegalPerson, (pr(businessName, APPSTRING, \varnothing), \\
& pr(street, APPSTRING, \varnothing), \\
& pr(city, APPSTRING, \varnothing)), pr(zip, APPSTRING, \varnothing)),
& cl("Address_tmp1", \varnothing, \varnothing)
& )
\end{align*}
\begin{align*}
t &= db(tab(Person, pk("Id"), col(surname, APPSTRING, \varnothing, \varnothing), \\
& col(street, APPSTRING, \varnothing, \varnothing), col(city, APPSTRING, \varnothing, \varnothing) \\
& col(zip, APPSTRING, \varnothing, \varnothing), \varnothing), \\
& tab(LegalPerson, pk("Id"),  col(businessName, APPSTRING, \varnothing, \varnothing), \\
& col(street, APPSTRING, \varnothing, \varnothing), col(city, APPSTRING, \varnothing, \varnothing) \\
& col(zip, APPSTRING, \varnothing, \varnothing), \varnothing), \\
& tab("Address_tmp1", pk("Id"), \varnothing, \varnothing)) 
\end{align*}
\begin{align*}
r &= row("person", ["Id", 1], ["surname", "Griffin"], \\
& ["street", "S. Mary Evenue 22"], ["city", "NY"], ["zip", 10001]), \\
& row("person", ["Id", 2], ["surname", "Doe"], \\
& ["street", "Olive ave. 2225"], ["city", "LA"], ["zip", 90003]), \\
& row("legalPerson", ["Id", 1], ["businessName", "Tools and Machines ltd."], \\
& ["street", "Hill stret 22"], ["city", "NY"], ["zip", 10001]), \\
& row("legalPerson", ["Id", 2], ["businessName", "Doe"], \\
& ["street", "Pine ave. 2225"], ["city", "LA"], ["zip", 90003]))
\end{align*}

\newpage
ExtactClass = copyProperty("street"
\begin{align*}
a' &= app(cl(Person, (pr(surname, APPSTRING, \varnothing), \\
& pr(street, APPSTRING, \varnothing), \\
& pr(city, APPSTRING, \varnothing)), pr(zip, APPSTRING, \varnothing)), \\
& cl(LegalPerson, (pr(businessName, APPSTRING, \varnothing), \\
& pr(street, APPSTRING, \varnothing), \\
& pr(city, APPSTRING, \varnothing)), pr(zip, APPSTRING, \varnothing)), \\
& cl("Address_tmp1", pr(street, APPSTRING, \varnothing) , \varnothing)
& )
\end{align*}
\begin{align*}
t &= db(tab(Person, pk("Id"), col(surname, APPSTRING, \varnothing, \varnothing), \\
& col(street, APPSTRING, \varnothing, \varnothing), col(city, APPSTRING, \varnothing, \varnothing) \\
& col(zip, APPSTRING, \varnothing, \varnothing), \varnothing), \\
& tab(LegalPerson, pk("Id"),  col(businessName, APPSTRING, \varnothing, \varnothing), \\
& col(street, APPSTRING, \varnothing, \varnothing), col(city, APPSTRING, \varnothing, \varnothing) \\
& col(zip, APPSTRING, \varnothing, \varnothing), \varnothing), \\
& tab("Address_tmp1", pk("Id"), col(street, APPSTRING, \varnothing, \varnothing),\\
& \varnothing)) 
\end{align*}
\begin{align*}
r &= \{ row("person", ["Id", 1], ["surname", "Griffin"], \\
& ["street", "S. Mary Evenue 22"], ["city", "NY"], ["zip", 10001]), \\
& row("person", ["Id", 2], ["surname", "Doe"], \\
& ["street", "Olive ave. 2225"], ["city", "LA"], ["zip", 90003]), \\
& row("legalPerson", ["Id", 1], ["businessName", "Tools and Machines ltd."], \\
& ["street", "Hill stret 22"], ["city", "NY"], ["zip", 10001]), \\
& row("legalPerson", ["Id", 2], ["businessName", "Doe"], \\
& ["street", "Pine ave. 2225"], ["city", "LA"], ["zip", 90003])\\
& row("address\_tmp1", ["Id", 1], ["street", "S. Mary Evenue 22"]) \\
& row("address\_tmp1", ["Id", 1], ["street", "Olive ave. 2225"] )\\
\}
\end{align*}

\newpage
ExtactClass = dropPropertyAndData("street"
\begin{align*}
a' &= app(cl(Person, (pr(surname, APPSTRING, \varnothing), \\
& pr(city, APPSTRING, \varnothing)), pr(zip, APPSTRING, \varnothing)), \\
& cl(LegalPerson, (pr(businessName, APPSTRING, \varnothing), \\
& pr(street, APPSTRING, \varnothing), \\
& pr(city, APPSTRING, \varnothing)), pr(zip, APPSTRING, \varnothing)), \\
& cl("Address_tmp1", pr(street, APPSTRING, \varnothing) , \varnothing)
& )
\end{align*}
\begin{align*}
t &= db(tab(Person, pk("Id"), col(surname, APPSTRING, \varnothing, \varnothing), \\
& col(city, APPSTRING, \varnothing, \varnothing) \\
& col(zip, APPSTRING, \varnothing, \varnothing), \varnothing), \\
& tab(LegalPerson, pk("Id"),  col(businessName, APPSTRING, \varnothing, \varnothing), \\
& col(street, APPSTRING, \varnothing, \varnothing), col(city, APPSTRING, \varnothing, \varnothing) \\
& col(zip, APPSTRING, \varnothing, \varnothing), \varnothing), \\
& tab("Address_tmp1", pk("Id"), col(street, APPSTRING, \varnothing, \varnothing),\\
& \varnothing)) 
\end{align*}
\begin{align*}
r &= \{ row("person", ["Id", 1], ["surname", "Griffin"], \\
& ["city", "NY"], ["zip", 10001]), \\
& row("person", ["Id", 2], ["surname", "Doe"], \\
& ["city", "LA"], ["zip", 90003]), \\
& row("legalPerson", ["Id", 1], ["businessName", "Tools and Machines ltd."], \\
& ["street", "Hill stret 22"], ["city", "NY"], ["zip", 10001]), \\
& row("legalPerson", ["Id", 2], ["businessName", "Doe"], \\
& ["street", "Pine ave. 2225"], ["city", "LA"], ["zip", 90003])\\
& row("address\_tmp1", ["Id", 1], ["street", "S. Mary Evenue 22"]) \\
& row("address\_tmp1", ["Id", 1], ["street", "Olive ave. 2225"] )\\
\}
\end{align*}

\newpage
ExtactClass = copyProperty("city"
\begin{align*}
a' &= app(cl(Person, (pr(surname, APPSTRING, \varnothing), \\
& pr(city, APPSTRING, \varnothing)), pr(zip, APPSTRING, \varnothing)), \\
& cl(LegalPerson, (pr(businessName, APPSTRING, \varnothing), \\
& pr(street, APPSTRING, \varnothing), \\
& pr(city, APPSTRING, \varnothing)), pr(zip, APPSTRING, \varnothing)), \\
& cl("Address_tmp1", pr(street, APPSTRING, \varnothing) pr(city, APPSTRING, \varnothing) , \varnothing)
& )
\end{align*}
\begin{align*}
t &= db(tab(Person, pk("Id"), col(surname, DBSTRING, \varnothing, \varnothing), \\
& col(city, DBSTRING, \varnothing, \varnothing) \\
& col(zip, DBSTRING, \varnothing, \varnothing), \varnothing), \\
& tab(LegalPerson, pk("Id"),  col(businessName, DBSTRING, \varnothing, \varnothing), \\
& col(street, DBSTRING, \varnothing, \varnothing), col(city, DBSTRING, \varnothing, \varnothing) \\
& col(zip, DBSTRING, \varnothing, \varnothing), \varnothing), \\
& tab("Address_tmp1", pk("Id"), col(street, DBSTRING, \varnothing, \varnothing),\\
& col(city, DBSTRING, \varnothing, \varnothing)
& \varnothing)) 
\end{align*}
\begin{align*}
r &= \{ row("person", ["Id", 1], ["surname", "Griffin"], \\
& ["city", "NY"], ["zip", 10001]), \\
& row("person", ["Id", 2], ["surname", "Doe"], \\
&  ["city", "LA"], ["zip", 90003]), \\
& row("legalPerson", ["Id", 1], ["businessName", "Tools and Machines ltd."], \\
& ["street", "Hill stret 22"], ["city", "NY"], ["zip", 10001]), \\
& row("legalPerson", ["Id", 2], ["businessName", "Doe"], \\
& ["street", "Pine ave. 2225"], ["city", "LA"], ["zip", 90003])\\
& row("address\_tmp1", ["Id", 1], ["street", "S. Mary Evenue 22"], ["city", "NY"]) \\
& row("address\_tmp1", ["Id", 1], ["street", "Olive ave. 2225"], ["city", "LA"] )\\
\}
\end{align*}

\newpage
ExtactClass = dropPropertyAndData("city"
\begin{align*}
a' &= app(cl(Person, (pr(surname, APPSTRING, \varnothing)), \\
& pr(zip, APPSTRING, \varnothing)), \\
& cl(LegalPerson, (pr(businessName, APPSTRING, \varnothing), \\
& pr(street, APPSTRING, \varnothing), \\
& pr(city, APPSTRING, \varnothing)), pr(zip, APPSTRING, \varnothing)), \\
& cl("Address_tmp1", pr(street, APPSTRING, \varnothing) pr(city, APPSTRING, \varnothing) , \varnothing)
& )
\end{align*}
\begin{align*}
t &= db(tab(Person, pk("Id"), col(surname, DBSTRING, \varnothing, \varnothing), \\
& col(zip, DBSTRING, \varnothing, \varnothing), \varnothing), \\
& tab(LegalPerson, pk("Id"),  col(businessName, DBSTRING, \varnothing, \varnothing), \\
& col(street, DBSTRING, \varnothing, \varnothing), col(city, DBSTRING, \varnothing, \varnothing) \\
& col(zip, DBSTRING, \varnothing, \varnothing), \varnothing), \\
& tab("Address_tmp1", pk("Id"), col(street, DBSTRING, \varnothing, \varnothing),\\
& col(city, DBSTRING, \varnothing, \varnothing)
& \varnothing)) 
\end{align*}
\begin{align*}
r &= \{ row("person", ["Id", 1], ["surname", "Griffin"], \\
& ["zip", 10001]), \\
& row("person", ["Id", 2], ["surname", "Doe"], \\
& ["zip", 90003]), \\
& row("legalPerson", ["Id", 1], ["businessName", "Tools and Machines ltd."], \\
& ["street", "Hill stret 22"], ["city", "NY"], ["zip", 10001]), \\
& row("legalPerson", ["Id", 2], ["businessName", "Doe"], \\
& ["street", "Pine ave. 2225"], ["city", "LA"], ["zip", 90003])\\
& row("address\_tmp1", ["Id", 1], ["street", "S. Mary Evenue 22"], ["city", "NY"]) \\
& row("address\_tmp1", ["Id", 1], ["street", "Olive ave. 2225"], ["city", "LA"] )\\
\}
\end{align*}

>>>>

\paragraph{Add association} Adding an association into a database is complicated because of already existing instances. When an association between classes is added the instances of both classes has to be connected on the database level via foreign key or connection table. The information about pairing has to be provided by the user in form of set of instances pairs, because the model does not contain enough information. 
\begin{align*}
& \mathbf{addAsociation} : Label \times Association \times (Row \times Row) \times State \rightarrow State \\
& \Psi(s, addAsociation(l, a, m_{l_1, l_2})) = application(s) \circ addAssoc(l, a) \\
& \Phi(s, addAsociation(l, a, m_{l_1, l_2})) = \\
& =\begin{cases}
	\inference{ \exists t_s, t_t \in tables(d) : name(t_s) = l\\ 		\wedge name(t_t) = reference(a) \\ \wedge \forall f \in foreignKeys(t_t) \cup columns(t_t) \\: name(f) \neq name(a) \\ startCardinality(a) \leq 1}{\begin{gathered}
		database(s) \\ \bullet addForeignKey(name(t_t), \rho(a,d), d) \\ \bullet \forall r \in m_{l_1, l_2} : \\
		insertValue(name(t_t), value(primaryKey(second(r))), [name(a), value(primaryKey(first(r)))])
	\end{gathered}}
 \\ \\
	\inference{ \exists t_s, t_t \in tables(d) : name(t_s) = l \\ \wedge name(t_t) = reference(a) \\ \wedge startCardinality(a) > 1}{\begin{gathered} 
	database(s) \bullet addTable(\rho(a,d),d) \\ \bullet \forall r \in m_{l, reference(a)} :
	\\ insertRow(\\ row(name(owningClass(a)) + name(a), \\ [name(t_s), value(primaryKey(first(r)))]\\ [name(t_t), value(primaryKey(second(r)))]))
	\end{gathered}} 
\end{cases}\\
& s \in Software, l_1, l_2 \in Label, m_{l, reference(a)} \wedge l_2 = reference(a)
\end{align*}

@@

\section{Case Study}
The case study demonstrates how the transformation helps with data evolution in real example of software evolution. There are two classes in our software $Person$ and $LegalPerson$ both of them contains information about address (street, city and zip code). To improve the design of code the class Address has to be created which associated with both original classes and contains the data already stored in the software. The initial situation:
\begin{align*}
&	S = sw(a, db(t,r))
\end{align*}
\begin{align*}
a &= app(cl(Person, (pr(surname, APPSTRING, \varnothing), \\
& pr(street, APPSTRING, \varnothing), \\
& pr(city, APPSTRING, \varnothing)), pr(zip, APPSTRING, \varnothing)), \\
& cl(LegalPerson, (pr(businessName, APPSTRING, \varnothing), \\
& pr(street, APPSTRING, \varnothing), \\
& pr(city, APPSTRING, \varnothing)), pr(zip, APPSTRING, \varnothing))
\end{align*}
\begin{align*}
t &= db(tab(Person, pk("Id"), col(surname, APPSTRING, \varnothing, \varnothing), \\
& col(street, APPSTRING, \varnothing, \varnothing), col(city, APPSTRING, \varnothing, \varnothing) \\
& col(zip, APPSTRING, \varnothing, \varnothing), \varnothing), \\
& tab(LegalPerson, pk("Id"),  col(businessName, APPSTRING, \varnothing, \varnothing), \\
& col(street, APPSTRING, \varnothing, \varnothing), col(city, APPSTRING, \varnothing, \varnothing) \\
& col(zip, APPSTRING, \varnothing, \varnothing), \varnothing)) 
\end{align*}
\begin{align*}
r &= row("person", ["Id", 1], ["surname", "Griffin"], \\
& ["street", "S. Mary Evenue 22"], ["city", "NY"], ["zip", 10001]), \\
& row("person", ["Id", 2], ["surname", "Doe"], \\
& ["street", "Olive ave. 2225"], ["city", "LA"], ["zip", 90003]), \\
& row("legalPerson", ["Id", 10], ["businessName", "Tools and Machines ltd."], \\
& ["street", "Hill stret 22"], ["city", "NY"], ["zip", 10001]), \\
& row("legalPerson", ["Id", 20], ["businessName", "Doe"], \\
& ["street", "Pine ave. 2225"], ["city", "LA"], ["zip", 90003]))
\end{align*}
The first evolution step is to create the address class for $Person$ and $LegalPerson$, then the temporary class can be merged together and finally the temporary class has to be renamed to $Address$:
\begin{align*}
& state(S) \oplus Extract("Person", "Address_tmp1", "street", "city", "zip") \\
& \oplus AddAssociation("Person", assoc("address", "Address_tmp1", 1, 1),\\ 
& \{(x,y)| x \in instances("Person", database(S)), \\
& y \in instances("Address_tmp1", database(S)) : pkVal(x) = pkVal(y) \}) \\
& \oplus Extract("LegalPerson", "Address_tmp2", "street", "city", "zip")  \\
& \oplus AddAssociation("LegalPerson", assoc("address", "Address_tmp1", 1, 1),\\ 
& \{(x,y)| x \in instances("LegalPerson", database(S)), \\
& y \in instances("Address_tmp2", database(S)) : pkVal(x) = pkVal(y) \}) \\
& \oplus Merge("Address_tmp1", "Address_tmp2", "Address") \\
& \oplus RemoveTableAndData("Address_tmp1") \\
& \oplus RemoveTableAndData("Address_tmp2")
\end{align*}
The software state after adding the second association is:

@@

\newpage
ExtactClass = addClass
\begin{align*}
a' &= app(cl(Person, (pr(surname, APPSTRING, \varnothing), \\
& pr(street, APPSTRING, \varnothing), \\
& pr(city, APPSTRING, \varnothing)), pr(zip, APPSTRING, \varnothing)), \\
& cl(LegalPerson, (pr(businessName, APPSTRING, \varnothing), \\
& pr(street, APPSTRING, \varnothing), \\
& pr(city, APPSTRING, \varnothing)), pr(zip, APPSTRING, \varnothing)),
& cl("Address_tmp1", \varnothing, \varnothing)
& )
\end{align*}
\begin{align*}
t &= db(tab(Person, pk("Id"), col(surname, APPSTRING, \varnothing, \varnothing), \\
& col(street, APPSTRING, \varnothing, \varnothing), col(city, APPSTRING, \varnothing, \varnothing) \\
& col(zip, APPSTRING, \varnothing, \varnothing), \varnothing), \\
& tab(LegalPerson, pk("Id"),  col(businessName, APPSTRING, \varnothing, \varnothing), \\
& col(street, APPSTRING, \varnothing, \varnothing), col(city, APPSTRING, \varnothing, \varnothing) \\
& col(zip, APPSTRING, \varnothing, \varnothing), \varnothing), \\
& tab("Address_tmp1", pk("Id"), \varnothing, \varnothing)) 
\end{align*}
\begin{align*}
r &= row("person", ["Id", 1], ["surname", "Griffin"], \\
& ["street", "S. Mary Evenue 22"], ["city", "NY"], ["zip", 10001]), \\
& row("person", ["Id", 2], ["surname", "Doe"], \\
& ["street", "Olive ave. 2225"], ["city", "LA"], ["zip", 90003]), \\
& row("legalPerson", ["Id", 10], ["businessName", "Tools and Machines ltd."], \\
& ["street", "Hill stret 22"], ["city", "NY"], ["zip", 10001]), \\
& row("legalPerson", ["Id", 20], ["businessName", "Doe"], \\
& ["street", "Pine ave. 2225"], ["city", "LA"], ["zip", 90003]))
\end{align*}

\newpage
ExtactClass = copyProperty("street"
\begin{align*}
a' &= app(cl(Person, (pr(surname, APPSTRING, \varnothing), \\
& pr(street, APPSTRING, \varnothing), \\
& pr(city, APPSTRING, \varnothing)), pr(zip, APPSTRING, \varnothing)), \\
& cl(LegalPerson, (pr(businessName, APPSTRING, \varnothing), \\
& pr(street, APPSTRING, \varnothing), \\
& pr(city, APPSTRING, \varnothing)), pr(zip, APPSTRING, \varnothing)), \\
& cl("Address_tmp1", pr(street, APPSTRING, \varnothing) , \varnothing)
& )
\end{align*}
\begin{align*}
t &= db(tab(Person, pk("Id"), col(surname, APPSTRING, \varnothing, \varnothing), \\
& col(street, APPSTRING, \varnothing, \varnothing), col(city, APPSTRING, \varnothing, \varnothing) \\
& col(zip, APPSTRING, \varnothing, \varnothing), \varnothing), \\
& tab(LegalPerson, pk("Id"),  col(businessName, APPSTRING, \varnothing, \varnothing), \\
& col(street, APPSTRING, \varnothing, \varnothing), col(city, APPSTRING, \varnothing, \varnothing) \\
& col(zip, APPSTRING, \varnothing, \varnothing), \varnothing), \\
& tab("Address_tmp1", pk("Id"), col(street, APPSTRING, \varnothing, \varnothing),\\
& \varnothing)) 
\end{align*}
\begin{align*}
r &= \{ row("person", ["Id", 1], ["surname", "Griffin"], \\
& ["street", "S. Mary Evenue 22"], ["city", "NY"], ["zip", 10001]), \\
& row("person", ["Id", 2], ["surname", "Doe"], \\
& ["street", "Olive ave. 2225"], ["city", "LA"], ["zip", 90003]), \\
& row("legalPerson", ["Id", 10], ["businessName", "Tools and Machines ltd."], \\
& ["street", "Hill stret 22"], ["city", "NY"], ["zip", 10001]), \\
& row("legalPerson", ["Id", 20], ["businessName", "Doe"], \\
& ["street", "Pine ave. 2225"], ["city", "LA"], ["zip", 90003])\\
& row("address\_tmp1", ["Id", 1], ["street", "S. Mary Evenue 22"]) \\
& row("address\_tmp1", ["Id", 1], ["street", "Olive ave. 2225"] )\\
\}
\end{align*}

\newpage
ExtactClass = dropPropertyAndData("street"
\begin{align*}
a' &= app(cl(Person, (pr(surname, APPSTRING, \varnothing), \\
& pr(city, APPSTRING, \varnothing)), pr(zip, APPSTRING, \varnothing)), \\
& cl(LegalPerson, (pr(businessName, APPSTRING, \varnothing), \\
& pr(street, APPSTRING, \varnothing), \\
& pr(city, APPSTRING, \varnothing)), pr(zip, APPSTRING, \varnothing)), \\
& cl("Address_tmp1", pr(street, APPSTRING, \varnothing) , \varnothing)
& )
\end{align*}
\begin{align*}
t &= db(tab(Person, pk("Id"), col(surname, APPSTRING, \varnothing, \varnothing), \\
& col(city, APPSTRING, \varnothing, \varnothing) \\
& col(zip, APPSTRING, \varnothing, \varnothing), \varnothing), \\
& tab(LegalPerson, pk("Id"),  col(businessName, APPSTRING, \varnothing, \varnothing), \\
& col(street, APPSTRING, \varnothing, \varnothing), col(city, APPSTRING, \varnothing, \varnothing) \\
& col(zip, APPSTRING, \varnothing, \varnothing), \varnothing), \\
& tab("Address_tmp1", pk("Id"), col(street, APPSTRING, \varnothing, \varnothing),\\
& \varnothing)) 
\end{align*}
\begin{align*}
r &= \{ row("person", ["Id", 1], ["surname", "Griffin"], \\
& ["city", "NY"], ["zip", 10001]), \\
& row("person", ["Id", 2], ["surname", "Doe"], \\
& ["city", "LA"], ["zip", 90003]), \\
& row("legalPerson", ["Id", 10], ["businessName", "Tools and Machines ltd."], \\
& ["street", "Hill stret 22"], ["city", "NY"], ["zip", 10001]), \\
& row("legalPerson", ["Id", 20], ["businessName", "Doe"], \\
& ["street", "Pine ave. 2225"], ["city", "LA"], ["zip", 90003])\\
& row("address\_tmp1", ["Id", 1], ["street", "S. Mary Evenue 22"]) \\
& row("address\_tmp1", ["Id", 1], ["street", "Olive ave. 2225"] )\\
\}
\end{align*}

\newpage
ExtactClass = copyProperty("city"
\begin{align*}
a' &= app(cl(Person, (pr(surname, APPSTRING, \varnothing), \\
& pr(city, APPSTRING, \varnothing)), pr(zip, APPSTRING, \varnothing)), \\
& cl(LegalPerson, (pr(businessName, APPSTRING, \varnothing), \\
& pr(street, APPSTRING, \varnothing), \\
& pr(city, APPSTRING, \varnothing)), pr(zip, APPSTRING, \varnothing)), \\
& cl("Address_tmp1", pr(street, APPSTRING, \varnothing) pr(city, APPSTRING, \varnothing) , \varnothing)
& )
\end{align*}
\begin{align*}
t &= db(tab(Person, pk("Id"), col(surname, DBSTRING, \varnothing, \varnothing), \\
& col(city, DBSTRING, \varnothing, \varnothing) \\
& col(zip, DBSTRING, \varnothing, \varnothing), \varnothing), \\
& tab(LegalPerson, pk("Id"),  col(businessName, DBSTRING, \varnothing, \varnothing), \\
& col(street, DBSTRING, \varnothing, \varnothing), col(city, DBSTRING, \varnothing, \varnothing) \\
& col(zip, DBSTRING, \varnothing, \varnothing), \varnothing), \\
& tab("Address_tmp1", pk("Id"), col(street, DBSTRING, \varnothing, \varnothing),\\
& col(city, DBSTRING, \varnothing, \varnothing)
& \varnothing)) 
\end{align*}
\begin{align*}
r &= \{ row("person", ["Id", 1], ["surname", "Griffin"], \\
& ["city", "NY"], ["zip", 10001]), \\
& row("person", ["Id", 2], ["surname", "Doe"], \\
&  ["city", "LA"], ["zip", 90003]), \\
& row("legalPerson", ["Id", 10], ["businessName", "Tools and Machines ltd."], \\
& ["street", "Hill stret 22"], ["city", "NY"], ["zip", 10001]), \\
& row("legalPerson", ["Id", 20], ["businessName", "Doe"], \\
& ["street", "Pine ave. 2225"], ["city", "LA"], ["zip", 90003])\\
& row("address\_tmp1", ["Id", 1], ["street", "S. Mary Evenue 22"], ["city", "NY"]) \\
& row("address\_tmp1", ["Id", 1], ["street", "Olive ave. 2225"], ["city", "LA"] )\\
\}
\end{align*}

\newpage
ExtactClass = dropPropertyAndData("city"
\begin{align*}
a' &= app(cl(Person, (pr(surname, APPSTRING, \varnothing)), \\
& pr(zip, APPSTRING, \varnothing)), \\
& cl(LegalPerson, (pr(businessName, APPSTRING, \varnothing), \\
& pr(street, APPSTRING, \varnothing), \\
& pr(city, APPSTRING, \varnothing)), pr(zip, APPSTRING, \varnothing)), \\
& cl("Address_tmp1", pr(street, APPSTRING, \varnothing) pr(city, APPSTRING, \varnothing) , \varnothing)
& )
\end{align*}
\begin{align*}
t &= db(tab(Person, pk("Id"), col(surname, DBSTRING, \varnothing, \varnothing), \\
& col(zip, DBSTRING, \varnothing, \varnothing), \varnothing), \\
& tab(LegalPerson, pk("Id"),  col(businessName, DBSTRING, \varnothing, \varnothing), \\
& col(street, DBSTRING, \varnothing, \varnothing), col(city, DBSTRING, \varnothing, \varnothing) \\
& col(zip, DBSTRING, \varnothing, \varnothing), \varnothing), \\
& tab("Address_tmp1", pk("Id"), col(street, DBSTRING, \varnothing, \varnothing),\\
& col(city, DBSTRING, \varnothing, \varnothing)
& \varnothing)) 
\end{align*}
\begin{align*}
r &= \{ row("person", ["Id", 1], ["surname", "Griffin"], \\
& ["zip", 10001]), \\
& row("person", ["Id", 2], ["surname", "Doe"], \\
& ["zip", 90003]), \\
& row("legalPerson", ["Id", 10], ["businessName", "Tools and Machines ltd."], \\
& ["street", "Hill stret 22"], ["city", "NY"], ["zip", 10001]), \\
& row("legalPerson", ["Id", 20], ["businessName", "Doe"], \\
& ["street", "Pine ave. 2225"], ["city", "LA"], ["zip", 90003])\\
& row("address\_tmp1", ["Id", 1], ["street", "S. Mary Evenue 22"], ["city", "NY"]) \\
& row("address\_tmp1", ["Id", 1], ["street", "Olive ave. 2225"], ["city", "LA"] )\\
\}
\end{align*}

\newpage
ExtactClass = CopyProperty("zip"
\begin{align*}
a' &= app(cl(Person, (pr(surname, APPSTRING, \varnothing)), \\
& pr(zip, APPSTRING, \varnothing)), \\
& cl(LegalPerson, (pr(businessName, APPSTRING, \varnothing), \\
& pr(street, APPSTRING, \varnothing), \\
& pr(city, APPSTRING, \varnothing)), pr(zip, APPSTRING, \varnothing)), \\
& cl("Address_tmp1", pr(street, APPSTRING, \varnothing) pr(city, APPSTRING, \varnothing), pr(zip, APPSTRING, \varnothing), \varnothing)
& )
\end{align*}
\begin{align*}
t &= db(tab(Person, pk("Id"), col(surname, DBSTRING, \varnothing, \varnothing), \\
& col(zip, DBSTRING, \varnothing, \varnothing), \varnothing), \\
& tab(LegalPerson, pk("Id"),  col(businessName, DBSTRING, \varnothing, \varnothing), \\
& col(street, DBSTRING, \varnothing, \varnothing), col(city, DBSTRING, \varnothing, \varnothing) \\
& col(zip, DBSTRING, \varnothing, \varnothing), \varnothing), \\
& tab("Address_tmp1", pk("Id"), col(street, DBSTRING, \varnothing, \varnothing),\\
& col(city, DBSTRING, \varnothing, \varnothing), col(zip, DBSTRING, \varnothing, \varnothing)
& \varnothing)) 
\end{align*}
\begin{align*}
r &= \{ row("person", ["Id", 1], ["surname", "Griffin"], \\
& ["zip", 10001]), \\
& row("person", ["Id", 2], ["surname", "Doe"], \\
& ["zip", 90003]), \\
& row("legalPerson", ["Id", 10], ["businessName", "Tools and Machines ltd."], \\
& ["street", "Hill stret 22"], ["city", "NY"], ["zip", 10001]), \\
& row("legalPerson", ["Id", 20], ["businessName", "Doe"], \\
& ["street", "Pine ave. 2225"], ["city", "LA"], ["zip", 90003])\\
& row("address\_tmp1", ["Id", 1], ["street", "S. Mary Evenue 22"], ["city", "NY"], ["zip", 10001]) \\
& row("address\_tmp1", ["Id", 1], ["street", "Olive ave. 2225"], ["city", "LA"], ["zip", 90003]) )\\
\}
\end{align*}
